\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliography}

\bibitem{zargar} S. T. Zargar, J. Joshi and D. Tipper: "A Survey of Defense Mechanisms Against Distributed Denial of Service (DDoS) Flooding Attacks," in IEEE Communications Surveys \& Tutorials, vol. 15, no. 4, pp. 2046-2069, \url{https://ieeexplore.ieee.org/document/6489876/citations?tabFilter=papers#citations}, Fourth Quarter 2013.

\bibitem{kamboj} P. Kamboj, M. C. Trivedi, V. K. Yadav and V. K. Singh: "Detection techniques of DDoS attacks: A survey," 2017 4th IEEE Uttar Pradesh Section International Conference on Electrical, Computer and Electronics (UPCON), Mathura,  pp. 675-679, \url{https://ieeexplore.ieee.org/document/8251130} 2017

\bibitem{yelizarov} Yelizarov, Anatoly \& Gamayunov, Dennis: "Visualization of complex attacks and state of attacked network". 6th International Workshop on Visualization for Cyber Security 2009, VizSec 2009 - Proceedings. 1 - 9. 10.1109/VIZSEC.2009.5375527 2009

\bibitem{wu} C. Wu, S. Sheng and X. Dong: "Research on Visualization Systems for DDoS Attack Detection," 2018 IEEE International Conference on Systems, Man, and Cybernetics (SMC), Miyazaki, Japan, pp. 2986-2991, \url{http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=8616503&isnumber=8615655} 2018, 
\bibitem{shiravi} H. Shiravi, A. Shiravi, and A. A. Ghorbani. "A survey of visualization systems for network security." \textit{IEEE Transactions on Visualization and Computer Graphics}, 18(8):1313-1329, Aug 2012. doi: 10.1109/TVCG.2011.144
\bibitem{chen} S. Chen, F. Merkle, H. Schaefer, C. Guo, H. Ai, X. Yuan, and T. Ertl. Vast 2013 mini challenge 3: Annette collaboration oriented visualization of network data.
\bibitem{lee} C. P. Lee, J. Trost, N. Gibbs, R. Beyah, and J. A. Copeland. Visual firewall: real-time network security monitor. In \textit{IEEE Workshop on Visualization for Computer Security}, 2005. (VizSEC 05)., pp. 129-136, Oct 2005. doi: 10.1109/VIZSEC.2005.1532075
\bibitem{yang} Y. J. Yang and Y. H. Liu. A dos attack situation visualization method based on parallel coordinates. In \textit{2012 IEEE 12th International Conference on Computer and Information Technology}, pp. 340-344, Oct 2012. doi: 10.1109/CIT.2012.85
\bibitem{zhangRadial} J. Zhang, G. Yang, L. Lu, M. Huang, and M. Che. A novel visualization method for detecting ddos network attacks. In \textit{Visual Information Communication}, pp. 185-194. Springer, 2009.
\bibitem{pearlman} J. Pearlman and P. Rheingans. Visualizing network security events using compound glyphs from a service-oriented perspective. In \textit{VizSEC 2007}, pp. 131-146. Springer, 2008.
\bibitem{barbosa} P. T. Barbosa and L. Z. Granville. Interactive snmp traffic analysis through information visualization. In \textit{2010 IEEE Network Operations and Management Symposium - NOMS 2010}, pp. 73-79, April 2010. doi: 10.1109/NOMS.2010.5488438
\bibitem{zhangCluster} J. Zhang and M. L. Huang. Visual analytics model for intrusion detection in flood attack. In \textit{2013 12th IEEE International Conference on Trust, Security and Privacy in Computing and Communications}, pp. 277-284, July 2013. doi: 10.1109/TrustCom.2013.38
\bibitem{choi} H. Choi, H. Lee, and H. Kim. Fast detection and visualization of network attacks on parallel coordinates. \textit{computers \& security}, 28(5):276-288, 2009.
\bibitem{okada} Y. Okada. Network data visualization using parallel coordinates version of time-tunnel with 2dto2d visualization for intrusion detection. In \textit{2013 27th International Conference on Advanced Information Networking and Applications Workshops}, pp. 1088-1093, March 2013. doi: 10. 1109/WAINA.2013.185
\bibitem{tcpdump} Manpage of TCPDUMP, \url{https://www.tcpdump.org/manpages/tcpdump.1.html}, last accessed 21.10.2019
\bibitem{ddosdb} DDoSDB ,\url{https://www.tcpdump.org/manpages/tcpdump.1.html}, last accessed 21.10.2019
\bibitem{ddosdb-help} DDoSDB , \url{https://ddosdb.org/help}, last accessed 22.10.2019
\bibitem{ddos_dissector} ddos-clearing-house/ddos\_dissector \url{https://github.com/ddos-clearing-house/ddos_dissector}, last accessed 22.10.2019
\bibitem{hostingtribunal.com} 39 Jaw-Dropping DDoS Statistics to Keep in Mind for 2019, \url{https://hostingtribunal.com/blog/ddos-statistics}, last accessed 24.11.2019
\bibitem{appliedsecurityvisualization} Raffael Marty: Applied Security Visualization, First Edition, Addison-Wesley Professional, 2008
\bibitem{teamcymru} IP-to-ASN - Team Cymru, \url{https://www.team-cymru.com/IP-ASN-mapping.html#whois}, last accessed 03.12.2019
\bibitem{geolite2} GeoLite2 Free Downloadable Databases « MaxMind Developer Site \url{https://dev.maxmind.com/geoip/geoip2/geolite2/#Databases}, last accessed 03.12.2019

\end{thebibliography}

